How is the Brazilian Amazon constructed as a problem at different levels? Amazonian

### 2022-02-10 20220210_Draft.Rmd
#todolistupdatedinrmd #random_sample.csvupdatedwithlivio'scommentonpuretypes #new_dictionary.docxcreatedwith commentstobediscussed

- Amazon context data up to date?
- Can we copy location stuff from previous set?
- Start improving dictionary: prepare sheet with large random sample of classified amazonian context for inductive analysis (speaker, year, context, classification)

>>>>

- operationalize 1st version of new dictionary.docx.
- solve broader problems mentioned in new dictionary.docx.
- spread context and classify based in new dictionary -> new iteration of random_sample and dictionary improvement.
